Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-10 WRITEUP/ms.tex
removed Drexel affiliation
change notation for eq 1

% --------------------------------------------
% \documentclass[twocolumn]{aastex6}
% \documentclass[apj]{emulateapj}
\documentclass[iop]{emulateapj} 
\usepackage{amsmath}

@@

\author{T. K. Daisy Leung\altaffilmark{1, 2}}
\author{Andrea Pallottini\altaffilmark{3, 4}}
\author{Andrea Ferrara\altaffilmark{4, 5}}
\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7, 8}}

\affil{\textsuperscript{1} Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; }
\email{tleung@astro.cornell.edu}
\altaffiltext{2}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Avenue, New York, NY 10010, USA}
\altaffiltext{3}{Centro Fermi, Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi'', Piazza del Viminale 1, Roma, 00184, Italy}
\altaffiltext{4}{Scuola Normale Superiore, Piazza dei Cavalieri 7, I-56126 Pisa, Italy}
\altaffiltext{5}{Kavli Institute for the Physics and Mathematics of the Universe (IPMU), The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa 277-8583, Japan}
\altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
\altaffiltext{7}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}
\altaffiltext{8}{Department of Physics, Disque Hall, Drexel University, Philadelphia, PA 19104, USA}

@@

The mass of an MC is calculated from the uniformly-gridded 3D density field,
integrating over all zones of the MC, multiplied by its volume. 
The size of an MC ($R$) is defined assuming spherical geometry (i.e., 
the size is parameterized via the radius of a sphere, which has a volume corresponding to that of the identified MC).
Since in \obs, dense gas contributes more to the observed linewidths than the more diffuse gas. We therefore calculate 
the one-dimensional non-thermal component of the velocity dispersion ($\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{xyz} \sum_{i}^N \rho_i \left(\mathbf{v} - \mathbf{\bar v}\right)_{xyz}^2}{\sum_i^N \rho_i},
\end{equation}
where $N$ is the number of zones of each MC.
The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\end{equation}
The local sound speed ($c_s$)
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities\footnote{We find comparable velocity dispersion between that derived from 
taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that
rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.
We further quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion ($\sigma$).}.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
\caption{
SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those 
observed in 0\,$\lesssim$\,\z$\lesssim$\,2 galaxies.
Literature data are compiled from \citealt{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a} and 
\citealt{Pallottini17b}.
%The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} 
%and references therein, and Sharon et al. in prep.
\label{fig:sk}}
\end{figure*}

>>>>

% --------------------------------------------
% \documentclass[twocolumn]{aastex6}
% \documentclass[apj]{emulateapj}
%\documentclass[iop]{emulateapj_old} 
\documentclass[iop]{emulateapj} 
\usepackage{amsmath}

@@

\author{T. K. Daisy Leung\altaffilmark{1, 2}}
\author{Andrea Pallottini\altaffilmark{3, 4}}
\author{Andrea Ferrara\altaffilmark{4, 5}}
\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7
%mm, 8   [I only use the Drexel affiliation when working with folks
%from there...]
}}

\affil{\textsuperscript{1} Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; }
\email{tleung@astro.cornell.edu}
\altaffiltext{2}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Avenue, New York, NY 10010, USA}
\altaffiltext{3}{Centro Fermi, Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi'', Piazza del Viminale 1, Roma, 00184, Italy}
\altaffiltext{4}{Scuola Normale Superiore, Piazza dei Cavalieri 7, I-56126 Pisa, Italy}
\altaffiltext{5}{Kavli Institute for the Physics and Mathematics of the Universe (IPMU), The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa 277-8583, Japan}
\altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
\altaffiltext{7}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}
%mm \altaffiltext{8}{Department of Physics, Disque Hall, Drexel University, Philadelphia, PA 19104, USA}

@@

The mass of an MC is calculated from the uniformly-gridded 3D density field,
integrating over all zones of the MC, multiplied by its volume. 
The size of an MC ($R$) is defined assuming spherical geometry (i.e., 
the size is parameterized via the radius of a sphere, which has a volume corresponding to that of the identified MC).
Since in \obs, dense gas contributes more to the observed linewidths than the more diffuse gas. We therefore calculate 
the one-dimensional non-thermal component of the velocity dispersion ($\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done over the cells composing each MC.
The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\end{equation}
The local sound speed ($c_s$)
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities\footnote{We find comparable velocity dispersion between that derived from 
taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that
rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.
We further quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion ($\sigma$).}.

@@

%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
%\caption{
%SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those 
%observed in 0\,$\lesssim$\,\z$\lesssim$\,2 galaxies.
%Literature data are compiled from \citealt{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a} and 
%\citealt{Pallottini17b}.
%%The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} 
%%and references therein, and Sharon et al. in prep.
%\label{fig:sk}}
%\end{figure*}
